% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

This work would not have been possible without the advice and support of many. Firstly, I want to thank my supervisor, Marco Di Natale, for having helped me to get into the domain of Model-Based Design and for having always been available to answer my questions. %Marco, I greatly appreciated your constructive criticism.

\paragraph{} I would like to thank my colleagues from my internship at United Technologies Research Centre, you supported me greatly and were always willing to help me. I would particularly like to thank my supervisor Phil Harris for giving me the opportunity to work at UTRC. Stylianos Basagiannis, I want to thank you for all of the opportunities I was given to conduct my work. Thanks to Juan Valverde-Alcala, without your patience and suggestions this thesis would be in a far earlier state.

%\paragraph{} In these last two years I took part of many activities, with countless people helping me every in step. I want to express my gratitude to all those friends. Thanks to 

\paragraph{} Lastly, I would like to thank all people expressed their support through their love, friendship and encouragement.
\par\textit{In questi ultimi due anni ho preso parte a tante attivit\`{a}, incontrando tante persone che mi hanno aiutato a ogni passo. Grazie ad Alex, Michele, Enrica, Jasmin, Martina, Angela, Chiara, Alessandra, Antonio, Michele, Elena, Salvatore, Antonello e Luca. Con voi ho passato tanti bei momenti, e anche nei periodi pi\`{u} difficili la vostra amicizia non \`{e} venuta meno.}
\par\textit{Grazie a te Sara, averti avuto affianco in questi ultimi due anni per me \`{e} stato fonte di grande forza. Grazie per aver supportato, e spesso sopportato, la mia voglia di fare. Niente sarebbe stato uguale senza di te.}
\par\textit{Grazie a tutti i parenti che mi hanno supportato, in particolare a zio Francesco, senza i tuoi insegnamenti non sarei chi sono oggi.}
\par \emph{Grazie a voi pap\`{a} e mamma. Siamo stati lontani ma il vostro aiuto non \`{e} mai venuto meno. Mi avete dato sempre tutto quello di cui avevo bisogno e di questo ve ne sono grato. Il futuro ci ripagher\`{a} dei nostri sacrifici.}


{\raggedleft\vfill\itshape\Longstack[l]{
  Pasquale Antonante\\
  Cork, April 2017
}\par
}


\end{acknowledgements}
